---
title: "p8105_hw5_qh2283"
output: github_document
date: "2023-11-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(purrr)
library(broom)
```

# Problem1

# Problem2

```{r}
#Start with a dataframe of all file names
file_names <- list.files(path = "data", full.names = TRUE, pattern = "\\.csv$")
#Read data and extract IDs and arms:
data_list <- map(file_names, ~{
  data <- read_csv(.x)
  file_info <- str_match(.x, "([a-z]+)_([0-9]+)") 
  data <- data %>% 
    mutate(subject_id = file_info[2],
           arm = file_info[1])
})

#Tidy the data
tidy_data <- map(data_list, ~pivot_longer(.x, cols = -c(subject_id, arm), names_to = "time", values_to = "observation"))
all_data <- bind_rows(tidy_data)

#Spaghetti plot
ggplot(all_data, aes(x = time, y = observation, group = subject_id, color = arm)) +
  geom_line() +
  theme_dark() +
  labs(title = "Observations Over Time by Subject", x = "Time", y = "Observation")

```
```{r}
# Problem3

```{r}
# Set design elements
n <- 30
sigma <- 5
mu_values <- 0:6
alpha <- 0.05
num_simulations <- 5000

# Function to perform simulations
simulate_power <- function(mu, n, sigma, num_simulations, alpha) {
  t_tests <- replicate(num_simulations, {
    sample_data <- rnorm(n, mean = mu, sd = sigma)
    t_test_result <- t.test(sample_data, mu = 0)
    tidy_t_test <- tidy(t_test_result)
    tidy_t_test
  }, simplify = FALSE) %>%
  bind_rows() %>%
  mutate(rejected = p.value < alpha)
  
  data.frame(
    mu = mu,
    power = mean(t_tests$rejected),
    mean_estimate = mean(t_tests$estimate),
    mean_estimate_rejected = mean(t_tests$estimate[t_tests$rejected])
  )
}

# Run simulation for each mu
results <- map_df(mu_values, ~simulate_power(., n, sigma, num_simulations, alpha))

# Plot the power vs true value of mu
ggplot(results, aes(x = mu, y = power)) +
  geom_point() +
  geom_line() +
  labs(title = "Power vs True Mean", x = "True Mean (mu)", y = "Power")

# Plot the average estimate of mu_hat
ggplot(results, aes(x = mu, y = mean_estimate)) +
  geom_point() +
  geom_line() +
  labs(title = "Average Estimate of mu_hat vs True Mean", x = "True Mean (mu)", y = "Average Estimate (mu_hat)")

# Overlay average estimate of mu_hat when null is rejected
ggplot(results, aes(x = mu)) +
  geom_point(aes(y = mean_estimate)) +
  geom_point(aes(y = mean_estimate_rejected), color = "red") +
  geom_line(aes(y = mean_estimate)) +
  geom_line(aes(y = mean_estimate_rejected), color = "red") +
  labs(title = "Average Estimate of mu_hat vs True Mean", x = "True Mean (mu)", y = "Average Estimate (mu_hat)")


```

